---
title: "brms:::loo.brmsfit"
author: "Kevin O Brien"
date: "1 November 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(brms)
```

loo.brmsfit Compute the LOO information criterion
#### Description 
Perform approximate leave-one-out cross-validation based on the posterior likelihood using the loo
package. for more details see loo.
Usage
## S3 method for class 'brmsfit'
loo(x, ..., compare = TRUE, resp = NULL,
pointwise = FALSE, reloo = FALSE, k_threshold = 0.7,
reloo_args = list(), model_names = NULL)
#### Arguments
x A fitted model object.
... More fitted model objects or further #### Arguments passed to the underlying postprocessing
functions.
compare A flag indicating if the information criteria of the models should be compared
to each other via compare_ic.
* `` resp``: Optional names of response variables. If specified, predictions are performed
only for the specified response variables.
pointwise A flag indicating whether to compute the full log-likelihood matrix at once or
separately for each observation. The latter approach is usually considerably
slower but requires much less working memory. Accordingly, if one runs into
memory issues, pointwise = TRUE is the way to go.
reloo Logical; Indicate whether reloo should be applied on problematic observations.
Defaults to FALSE.
k_threshold The threshold at which pareto k estimates are treated as problematic. Defaults to
0.7. Only used if argument reloo is TRUE. See pareto_k_ids for more details.
reloo_args Optional list of additional #### Arguments passed to reloo.
model_names If NULL (the default) will use model names derived from deparsing the call. Otherwise
will use the passed values as model names.
loo.brmsfit 89
#### Details
When comparing models fitted to the same data, the smaller the LOO, the better the fit. For brmsfit
objects, LOO is an alias of loo. Use method add_ic to store information criteria in the fitted model
object for later usage.
#### Value
If just one object is provided, an object of class ic. If multiple objects are provided, an object of
class iclist.

#### Examples
```{r}
## Not run:
# model with population-level effects only
fit1 <- brm(rating ~ treat + period + carry,
data = inhaler, family = "gaussian")
loo(fit1)
# model with an additional varying intercept for subjects
fit2 <- brm(rating ~ treat + period + carry + (1|subject),
data = inhaler, family = "gaussian")
# compare both models
loo(fit1, fit2)
## End(Not run)
```

#### Author(s)
Paul-Christian Buerkner <paul.buerkner@gmail.com>
References
Vehtari, A., Gelman, A., & Gabry J. (2016). Practical Bayesian model evaluation using leaveone-
out cross-validation and WAIC. In Statistics and Computing, doi:10.1007/s11222-016-9696-4.
arXiv preprint arXiv:1507.04544.
Gelman, A., Hwang, J., & Vehtari, A. (2014). Understanding predictive information criteria for
Bayesian models. Statistics and Computing, 24, 997-1016.
Watanabe, S. (2010). Asymptotic equivalence of Bayes cross validation and widely applicable
information criterion in singular learning theory. The Journal of Machine Learning Research, 11,
3571-3594.
