
bayes_R2.brmsfit Compute a Bayesian version of R-squared for regression models
#### Description 
Compute a Bayesian version of R-squared for regression models
bayes_R2.brmsfit 13
Usage
## S3 method for class 'brmsfit'
bayes_R2(object, resp = NULL, summary = TRUE,
robust = FALSE, probs = c(0.025, 0.975), ...)
#### Arguments
* ``object``: An object of class brmsfit.
* `` resp``: Optional names of response variables. If specified, predictions are performed
only for the specified response variables.
summary Should summary statistics (i.e. means, sds, and 95% intervals) be returned instead
of the raw values? Default is TRUE.
robust If FALSE (the default) the mean is used as the measure of central tendency and
the standard deviation as the measure of variability. If TRUE, the median and the
median absolute deviation (MAD) are applied instead. Only used if summary is
TRUE.
probs The percentiles to be computed by the quantile function. Only used if summary
is TRUE.
* `` ... ``: Further arguments passed to fitted, which is used in the computation of the
R-squared values.
#### Details
For an introduction to the approach, see https://github.com/jgabry/bayes_R2/blob/master/
bayes_R2.pdf.
#### Value
If summary = TRUE a 1 x C matrix is returned (C = length(probs) + 2) containing summary
statistics of Bayesian R-squared values. If summary = FALSE the posterior samples of the R-squared
#### Values are returned in a S x 1 matrix (S is the number of samples).
#### Examples 

```{r}
## Not run:
fit <- brm(mpg ~ wt + cyl, data = mtcars)
summary(fit)
bayes_R2(fit)
# compute R2 with new data
nd <- data.frame(mpg = c(10, 20, 30), wt = c(4, 3, 2), cyl = c(8, 6, 4))
bayes_R2(fit, newdata = nd)
## End(Not run)
14 bridge_sampler.brmsfit
bridge_sampler.brmsfit
Log Marginal Likelihood via Bridge Sampling
#### Description 
Computes log marginal likelihood via bridge sampling, which can be used in the computation of
bayes factors and posterior model probabilities. The brmsfit method is just a thin wrapper around
the corresponding method for stanfit objects.
Usage
## S3 method for class 'brmsfit'
bridge_sampler(samples, ...)
#### Arguments
samples A brmsfit object.
... Additional arguments passed to bridge_sampler.stanfit.
#### Details
Computing the marginal likelihood requires samples of all variables defined in Stan’s parameters
block to be saved. Otherwise bridge_sampler cannot be computed. Thus, please set save_all_pars = TRUE
in the call to brm, if you are planning to apply bridge_sampler to your models.
The computation of marginal likelihoods based on bridge sampling requires a lot more posterior
samples than usual. A good conservative rule of thump is perhaps 10-fold more samples (read:
the default of 4000 samples may not be enough in many cases). If not enough posterior samples
are provided, the bridge sampling algorithm tends to be unstable leading to considerably different
results each time it is run. We thus recommend running bridge_sampler multiple times to check
the stability of the results.
More details are provided under bridgesampling:bridge_sampler.
See Also
bayes_factor, post_prob
#### Examples 
```{r}

```{r}
## Not run:
# model with the treatment effect
fit1 <- brm(
count ~ log_Age_c + log_Base4_c + Trt_c,
data = epilepsy, family = negbinomial(),
prior = prior(normal(0, 1), class = b),
save_all_pars = TRUE
)

summary(fit1)
bridge_sampler(fit1)
```

```{r}
# model without the treatment effect
fit2 <- brm(
count ~ log_Age_c + log_Base4_c,
data = epilepsy, family = negbinomial(),
prior = prior(normal(0, 1), class = b),
save_all_pars = TRUE
)
summary(fit2)
bridge_sampler(fit2)
## End(Not run)
```

