---
title: "loo_model_weights.brmsfit"
author: "Kevin O Brien"
date: "1 November 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(brms)
```

loo_model_weights.brmsfit
Model averaging via stacking or pseudo-BMA weighting.
#### Description 
Compute model weights for brmsfit objects via stacking or pseudo-BMA weighting. For more details, see loo::loo_model_weights.

#### Usage
<pre><code>
## S3 method for class 'brmsfit'
loo_model_weights(x, ..., model_names = NULL)
</code></pre>

#### Arguments
* x A fitted model object.
* ... More fitted model objects or further #### Arguments passed to the underlying postprocessing functions.
* model_names If NULL (the default) will use model names derived from deparsing the call. Otherwise will use the passed values as model names.

#### Value

A named vector of model weights.

### Examples

```{r}
## Not run:
# model with population-level effects only
fit1 <- brm(rating ~ treat + period + carry,
data = inhaler, family = "gaussian")
# model with an additional varying intercept for subjects
fit2 <- brm(rating ~ treat + period + carry + (1|subject),
data = inhaler, family = "gaussian")
loo_model_weights(fit1, fit2)
## End(Not run)
```