---
title: "brms"
author: "Kevin O Brien"
date: "1 November 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


loo_predict.brmsfit Compute Weighted Expectations Using LOO
#### Description 
These functions are wrappers around the E_loo function of the loo package.

Usage

<pre><code>
## S3 method for class 'brmsfit'
loo_predict(object, type = c("mean", "var",
"quantile"), probs = 0.5, psis_object = NULL, resp = NULL, ...)
## S3 method for class 'brmsfit'
loo_linpred(object, type = c("mean", "var",
"quantile"), probs = 0.5, psis_object = NULL, resp = NULL,
scale = "linear", ...)
## S3 method for class 'brmsfit'
loo_predictive_interval(object, prob = 0.9,
psis_object = NULL, ...)
</code></pre>

#### Arguments
* object An object of class brmsfit.
* type The statistic to be computed on the results. Can by either "mean" (default),
"var", or "quantile".
* probs A vector of quantiles to compute. Only used if type = quantile.
* psis_object An optional object returend by psis. If psis_object is missing then psis is executed internally, which may be time consuming for models fit to very large datasets.
* `` resp``: Optional names of response variables. If specified, predictions are performed
only for the specified response variables.
* ... Optional arguments passed to the underlying methods that is log_lik, as well as predict or fitted.
* scale Passed to fitted.
* prob For loo_predictive_interval, a scalar in (0; 1) indicating the desired probability mass to include in the intervals. The default is prob = 0.9 (90% intervals).

#### Value
loo_predict and loo_linpred return a vector with one element per observation. The only exception is if type = "quantile" and length(probs) >= 2, in which case a separate vector for each

element of probs is computed and they are returned in a matrix with length(probs) rows and one column per observation.
loo_predictive_interval returns a matrix with one row per observation and two columns. loo_predictive_interval(..., is equivalent to loo_predict(..., type = "quantile", probs = c(a, 1-a)) with a = (1 - p)/2,
except it transposes the result and adds informative column names.

#### Examples

```{r}
## Not run:
## data from help("lm")
ctl <- c(4.17,5.58,5.18,6.11,4.50,4.61,5.17,4.53,5.33,5.14)
trt <- c(4.81,4.17,4.41,3.59,5.87,3.83,6.03,4.89,4.32,4.69)
d <- data.frame(
weight = c(ctl, trt),
group = gl(2, 10, 20, labels = c("Ctl", "Trt"))
)
fit <- brm(weight ~ group, data = d)
loo_predictive_interval(fit, prob = 0.8)
## optionally log-weights can be pre-computed and reused
psis <- loo::psis(-log_lik(fit), cores = 2)
loo_predictive_interval(fit, prob = 0.8, psis_object = psis)
loo_predict(fit, type = "var", psis_object = psis)
```
