fixef.brmsfit Extract Population-Level Estimates
#### Description 
Extract the population-level (’fixed’) effects from a brmsfit object.

#### Usage
<pre><code>
## S3 method for class 'brmsfit'
fixef(object, summary = TRUE, robust = FALSE,
probs = c(0.025, 0.975), pars = NULL, ...)
</code></pre>
#### Arguments

object An object of class brmsfit.
summary Should summary statistics (i.e. means, sds, and 95% intervals) be returned instead
of the raw values? Default is TRUE.
robust If FALSE (the default) the mean is used as the measure of central tendency and
the standard deviation as the measure of variability. If TRUE, the median and the
median absolute deviation (MAD) are applied instead. Only used if summary is
TRUE.
Frechet 63
probs The percentiles to be computed by the quantile function. Only used if summary
is TRUE.
pars Optional names of coefficients to extract. By default, all coefficients are extracted.
... Currently ignored.
value
If summary is TRUE, a matrix with one row per population-level effect and one column per calculated
estimate. If summary is FALSE, a matrix with one row per posterior sample and one column per
population-level effect.
Author(s)
Paul-Christian Buerkner <paul.buerkner@gmail.com>

#### Examples 
```{r}
## Not run:
fit <- brm(time | cens(censored) ~ age + sex + disease,
data = kidney, family = "exponential")
fixef(fit)
# extract only some coefficients
fixef(fit, pars = c("age", "sex"))
## End(Not run)
Frechet The Frechet Distribution
#### Description 
Density, distribution function, quantile function and random generation for the Frechet distribution
with location loc, scale scale, and shape shape.

#### Usage
<pre><code>
dfrechet(x, loc = 0, scale = 1, shape = 1, log = FALSE)
pfrechet(q, loc = 0, scale = 1, shape = 1, lower.tail = TRUE,
log.p = FALSE)
qfrechet(p, loc = 0, scale = 1, shape = 1, lower.tail = TRUE,
log.p = FALSE)
rfrechet(n, loc = 0, scale = 1, shape = 1)
64 GenExtremevalue
</code></pre>
#### Arguments

x, q Vector of quantiles.
loc Vector of locations.
scale Vector of scales.
shape Vector of shapes.
log Logical; If TRUE, values are returned on the log scale.
lower.tail Logical; If TRUE (default), return P(X <= x). Else, return P(X > x) .
log.p Logical; If TRUE, values are returned on the log scale.
p Vector of probabilities.
n Number of samples to draw from the distribution.
#### Details
See vignette("brms_families") for #### Details on the parameterization.
get_prior Overview on Priors for brms Models
#### Description 
Get information on all parameters (and parameter classes) for which priors may be specified including
default priors.

#### Usage
<pre><code>
get_prior(formula, data, family = gaussian(), autocor = NULL,
internal = FALSE)
</code></pre>
#### Arguments

* ``formula``: An object of class formula, brmsformula, or mvbrmsformula (or one that can
be coerced to that classes): A symbolic #### Description  of the model to be fitted.
The details of model specification are explained in brmsformula.
data An object of class data.frame (or one that can be coerced to that class) containing
data of all variables used in the model.
* `` family`` A description  of the response distribution and link function to be used in the
model. This can be a family function, a call to a family function or a character
string naming the family. Every family function has a link argument allowing to
specify the link function to be applied on the response variable. If not specified,
default links are used. For #### Details of supported families see brmsfamily. By
default, a linear gaussian model is applied. In multivariate models, family
might also be a list of families.
* ``autocor`` An optional cor_brms object describing the correlation structure within the response
variable (i.e., the ’autocorrelation’). See the documentation of cor_brms
for a #### Description  of the available correlation structures. Defaults to NULL, corresponding
to no correlations. In multivariate models, autocor might also be a
list of autocorrelation structures.
internal A flag indicating if the names of additional internal parameters should be displayed.
Setting priors on these parameters is not recommended
value
A data.frame with columns prior, class, coef, and group and several rows, each providing information
on a parameter (or parameter class) on which priors can be specified. The prior column is
empty except for internal default priors.
See Also
set_prior
66 gp

#### Examples 
```{r}
## get all parameters and parameters classes to define priors on
(prior <- get_prior(count ~ log_Age_c + log_Base4_c * Trt_c
+ (1|patient) + (1|visit),
data = epilepsy, family = poisson()))
## define a prior on all population-level effects a once
prior$prior[1] <- "normal(0,10)"
## define a specific prior on the population-level effect of Trt_c
prior$prior[5] <- "student_t(10, 0, 5)"
## verify that the priors indeed found their way into Stan's model code
make_stancode(count ~ log_Age_c + log_Base4_c * Trt_c
+ (1|patient) + (1|visit),
data = epilepsy, family = poisson(),
prior = prior)
```


horseshoe Set up a horseshoe prior in brms
#### Description 
Function used to set up a horseshoe prior for population-level effects in brms. The function does
not evaluate its </code></pre>
#### Arguments
 – it exists purely to help set up the model.

#### Usage
<pre><code>
horseshoe(df = 1, scale_global = 1, df_global = 1, scale_slab = 2,
df_slab = 4, par_ratio = NULL, autoscale = TRUE)
</code></pre>
#### Arguments

df Degrees of freedom of student-t prior of the local shrinkage parameters. Defaults
to 1.
scale_global Scale of the student-t prior of the global shrinkage parameter. Defaults to 1.
In linear models, scale_global will internally be multiplied by the residual
standard deviation parameter sigma.
df_global Degrees of freedom of student-t prior of the global shrinkage parameter. Defaults
to 1.
scale_slab Scale of the student-t prior of the regularization parameter. Defaults to 2.
df_slab Degrees of freedom of the student-t prior of the regularization parameter. Defaults
to 4.
par_ratio Ratio of the expected number of non-zero coefficients to the expected number of
zero coefficients. If specified, scale_global is ignored and internally computed
as par_ratio / sqrt(N), where N is the total number of observations in the
data.
70 horseshoe
autoscale Logical; indicating whether the horseshoe prior should be scaled using the residual
standard deviation sigma if possible and sensible (defaults to TRUE). Autoscaling
is not applied for distributional parameters or when the model does
not contain the parameter sigma.
#### Details
The horseshoe prior is a special shrinkage prior initially proposed by Carvalho et al. (2009). It
is symmetric around zero with fat tails and an infinitely large spike at zero. This makes it ideal
for sparse models that have many regression coefficients, although only a minority of them is nonzero.
The horseshoe prior can be applied on all population-level effects at once (excluding the
intercept) by using set_prior("horseshoe(1)"). The 1 implies that the student-t prior of the local
shrinkage parameters has 1 degrees of freedom. This may, however, lead to an increased number
of divergent transition in Stan. Accordingly, increasing the degrees of freedom to slightly higher
values (e.g., 3) may often be a better option, although the prior no longer resembles a horseshoe in
this case. Further, the scale of the global shrinkage parameter plays an important role in amount
of shrinkage applied. It defaults to 1, but this may result in too few shrinkage (Piironen & Vehtari,
2016). It is thus possible to change the scale using argument scale_global of the horseshoe
prior, for instance horseshoe(1, scale_global = 0.5). In linear models, scale_global will
internally be multiplied by the residual standard deviation parameter sigma. See Piironen and
Vehtari (2016) for recommendations how to properly set the global scale. The degrees of freedom
of the global shrinkage prior may also be adjusted via argument df_global. Piironen and Vehtari
(2017) recommend to specifying the ratio of the expected number of non-zero coefficients to the
expected number of zero coefficients par_ratio rather than scale_global directly. As proposed
by Piironen and Vehtari (2017), an additional regularization is applied that only affects non-zero
coefficients. The amount of regularization can be controlled via scale_slab and df_slab. To
make sure that shrinkage can equally affect all coefficients, predictors should be one the same
scale. Generally, models with horseshoe priors a more likely than other models to have divergent
transitions so that increasing adapt_delta from 0.8 to values closer to 1 will often be necessary.
See the documentation of brm for instructions on how to increase adapt_delta.
value
A character string obtained by match.call() with additional </code></pre>
#### Arguments
.
References
Carvalho, C. M., Polson, N. G., & Scott, J. G. (2009). Handling sparsity via the horseshoe. In
International Conference on Artificial Intelligence and Statistics (pp. 73-80).
Piironen J. & Vehtari A. (2016). On the Hyperprior Choice for the Global Shrinkage Parameter in
the Horseshoe Prior. https://arxiv.org/pdf/1610.05559v1.pdf
Piironen, J., and Vehtari, A. (2017). Sparsity information and regularization in the horseshoe and
other shrinkage priors. https://arxiv.org/abs/1707.01694
See Also
set_prior
Hurdle 71

#### Examples 
```{r}
set_prior(horseshoe(df = 3, par_ratio = 0.1))


