brmsformula Set up a model formula for use in brms
#### Description 
Set up a model formula for use in the brms package allowing to define (potentially non-linear)
additive multilevel models for all parameters of the assumed response distribution.
Usage
<pre><code>
brmsformula(formula, ..., flist = NULL, family = NULL,
autocor = NULL, nl = NULL, loop = NULL, cmc = NULL)
</code></pre>

#### Arguments

* formula An object of class formula (or one that can be coerced to that class): a symbolic
description  of the model to be fitted. The #### Details of model specification are given
in ’Details’.
* ... Additional formula objects to specify predictors of non-linear and distributional
parameters. Formulas can either be named directly or contain names
on their left-hand side. The following are distributional parameters of specific
families (all other parameters are treated as non-linear parameters): sigma
(residual standard deviation or scale of the gaussian, student, skew_normal,
lognormal exgaussian, and asym_laplace families); shape (shape parameter
of the Gamma, weibull, negbinomial, and related zero-inflated / hurdle
families); nu (degrees of freedom parameter of the student and frechet families);
phi (precision parameter of the beta and zero_inflated_beta families);
kappa (precision parameter of the von_mises family); beta (mean parameter
of the exponential component of the exgaussian family); quantile (quantile
parameter of the asym_laplace family); zi (zero-inflation probability); hu
(hurdle probability); zoi (zero-one-inflation probability); coi (conditional oneinflation
probability); disc (discrimination) for ordinal models; bs, ndt, and
bias (boundary separation, non-decision time, and initial bias of the wiener
diffusion model). By default, distributional parameters are modeled on the log
* scale if they can be positive only or on the logit scale if the can only be within
the unit interval. See ’#### Details’ for more explanation.
* flist Optional list of formulas, which are treated in the same way as formulas passed
via the ... argument.
* family Same argument as in brm. If family is specified in brmsformula, it will overwrite the value specified in brm.
* autocor Same argument as in brm. If autocor is specified in brmsformula, it will overwrite the value specified in brm.
* nl Logical; Indicates whether formula should be treated as specifying a non-linear model. 
By default, formula is treated as an ordinary linear model formula.
loop Logical; Only used in non-linear models. Indicates if the computation of the
non-linear formula should be done inside (TRUE) or outside (FALSE) a loop over
observations. Defaults to TRUE.
cmc Logical; Indicates whether automatic cell-mean coding should be enabled when
removing the intercept by adding 0 to the right-hand of model formulas. Defaults
to TRUE to mirror the behavior of standard R formula parsing.


brmsformula 33
#### Value
An object of class brmsformula, which is essentially a list containing all model formulas as well
as some additional information.
See Also
mvbrmsformula, brmsformula-helpers

Examples
```{r}
# multilevel model with smoothing terms
brmsformula(y ~ x1*x2 + s(z) + (1+x1|1) + (1|g2))
# additionally predict 'sigma'
brmsformula(y ~ x1*x2 + s(z) + (1+x1|1) + (1|g2),
sigma ~ x1 + (1|g2))
```

```{r}
# use the shorter alias 'bf'
(formula1 <- brmsformula(y ~ x + (x|g)))
(formula2 <- bf(y ~ x + (x|g)))
# will be TRUE
identical(formula1, formula2)
# incorporate censoring
bf(y | cens(censor_variable) ~ predictors)
```

```{r}
# define a simple non-linear model
bf(y ~ a1 - a2^x, a1 + a2 ~ 1, nl = TRUE)
# predict a1 and a2 differently
bf(y ~ a1 - a2^x, a1 ~ 1, a2 ~ x + (x|g), nl = TRUE)
# correlated group-level effects across parameters
bf(y ~ a1 - a2^x, a1 ~ 1 + (1|2|g), a2 ~ x + (x|2|g), nl = TRUE)
# define a multivariate model
bf(cbind(y1, y2) ~ x * z + (1|g))
```

```{r}
# define a zero-inflated model
# also predicting the zero-inflation part
bf(y ~ x * z + (1+x|ID1|g), zi ~ x + (1|ID1|g))
# specify a predictor as monotonic
bf(y ~ mo(x) + more_predictors)
# for ordinal models only
```

```{r}
# specify a predictor as category specific
bf(y ~ cs(x) + more_predictors)
# add a category specific group-level intercept
bf(y ~ cs(x) + (cs(1)|g))
# specify parameter 'disc'
bf(y ~ person + item, disc ~ item)
```

```{r}
# specify variables containing measurement error
bf(y ~ me(x, sdx))
# specify predictors on all parameters of the wiener diffusion model
# the main formula models the drift rate 'delta'
bf(rt | dec(decision) ~ x, bs ~ x, ndt ~ x, bias ~ x)
# fix the bias parameter to 0.5
bf(rt | dec(decision) ~ x, bias = 0.5)
# specify different predictors for different mixture components
mix <- mixture(gaussian, gaussian)
bf(y ~ 1, mu1 ~ x, mu2 ~ z, family = mix)
```

```{r}
# fix both residual standard deviations to the same #### Value
bf(y ~ x, sigma2 = "sigma1", family = mix)
# use the '+' operator to specify models
bf(y ~ 1) +
nlf(sigma ~ a * exp(b * x), a ~ x) +
lf(b ~ z + (1|g), dpar = "sigma") +
gaussian()
```

```{r}
# specify a multivariate model using the '+' operator
bf(y1 ~ x + (1|g)) +
gaussian() + cor_ar(~1|g) +
bf(y2 ~ z) + poisson()
# model missing values in predictors
bf(bmi ~ age * mi(chl)) +
bf(chl | mi() ~ age) +
set_rescor(FALSE)
```
