---
title: "``loo_R2.brmsfit`` Compute a LOO-adjusted R-squared for regression models"
author: "Kevin O Brien"
date: "1 November 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(brms)
```



#### Description 
Compute a LOO-adjusted R-squared for regression models

Usage
<pre><code>
## S3 method for class 'brmsfit'
loo_R2(object, resp = NULL, ...)
</code></pre>

#### Arguments
* `` object``: An object of class brmsfit.
* `` resp``: Optional names of response variables. If specified, predictions are performed only for the specified response variables.
* `` ... ``: Further arguments passed to fitted and log_lik, which are used in the computation of the R-squared values.

#### Value
A real value per response variable indicating the LOO-adjusted R-squared.

#### Examples


```{r}
fit <- brm(mpg ~ wt + cyl, data = mtcars)
summary(fit)
loo_R2(fit)
# compute R2 with new data
nd <- data.frame(mpg = c(10, 20, 30), wt = c(4, 3, 2), cyl = c(8, 6, 4))
loo_R2(fit, newdata = nd)
## End(Not run)
```