---
title: "``loo_model_weights.brmsfit``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(brms)
```

Model averaging via stacking or pseudo-BMA weighting.
#### Description 
Compute model weights for brmsfit objects via stacking or pseudo-BMA weighting. For more details, see ``loo::loo_model_weights``.

#### Usage
<pre><code>
## S3 method for class 'brmsfit'
loo_model_weights(x, ..., model_names = NULL)
</code></pre>

#### Arguments
* ``x``: A fitted model object.
* ``...``: More fitted model objects or further #### Arguments passed to the underlying postprocessing functions.
* ``model_names``: If NULL (the default) will use model names derived from deparsing the call. Otherwise will use the passed values as model names.



### Examples

```{r}
# model with population-level effects only
fit1 <- brm(rating ~ treat + period + carry,
data = inhaler, family = "gaussian")
```

```{r}
# model with an additional varying intercept for subjects
fit2 <- brm(rating ~ treat + period + carry + (1|subject),
data = inhaler, family = "gaussian")
loo_model_weights(fit1, fit2)
```
#### Value

A named vector of model weights.
