`` gr``  Set up basic grouping terms in brms
#### Description 
Function used to set up a basic grouping term in brms. The function does not evaluate its </code></pre>
#### Arguments

– it exists purely to help set up a model with grouping terms. gr is called implicitly inside the package and there is usually no need to call it directly.

#### Usage
<pre><code>
gr(..., by = NULL, dist = "gaussian")
</code></pre>

#### Arguments
* `` ...`` : One or more terms containing grouping factors.
* `` by`` : An optional factor variable, specifying sub-populations of the groups. For each level of the by variable, a separate variance-covariance matrix will be fitted. Levels of the grouping factor must be nested in levels of the by variable.
* `` dist`` : Name of the distribution of the group-level effects. Currently "gaussian" is the only option.



#### Examples 
```{r}
# model using basic lme4-style formula
fit1 <- brm(count ~ Trt + (1|patient), data = epilepsy)
summary(fit1)
```

```{r}
# equivalent model using 'gr' which is called anyway internally
fit2 <- brm(count ~ Trt + (1|gr(patient)), data = epilepsy)
summary(fit2)
```

```{r}
# include Trt as a by variable
fit3 <- brm(count ~ Trt + (1|gr(patient, by = Trt)), data = epilepsy)
summary(fit3)

```
#### See Also
brmsformula
