---
title: "``make_conditions`` Prepare Fully Crossed Conditions"
output: html_document
---
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


#### Description 
This is a helper function to prepare fully crossed conditions primarily for use with the conditions
argument of marginal_effects. Automatically creates labels for each row in the cond__ column.

#### Usage
<pre><code>
make_conditions(x, vars, ...)
</code></pre>
  
#### Arguments
* x An R object from which to extract the variables that should be part of the conditions.
* vars Names of the variables that should be part of the conditions.
* ... arguments passed to rows2labels.

#### Details
For factor like variables, all levels are used as conditions. For numeric variables, mean + (-1:1) * SD
are used as conditions.

#### Value
A data.frame where each row indicates a condition.
See Also
marginal_effects, rows2labels
94 make_stancode
Examples

```{r}

df <- data.frame(x = c("a", "b"), y = rnorm(10))
make_conditions(df, vars = c("x", "y"))
```
