---
title: "``pairs.brmsfit `` "
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(brms)

```

Create a matrix of output plots from a brmsfit object

#### Description 
A pairs method that is customized for MCMC output.

#### Usage
<pre><code>
## S3 method for class 'brmsfit'
pairs(x, pars = NA, exact_match = FALSE, ...)
</code></pre>

#### Arguments
* x An object of class brmsfit
* pars Names of parameters for which posterior samples should be returned, as given by a character vector or regular expressions. By default, all posterior samples of all parameters are extracted.
* exact_match Indicates whether parameter names should be matched exactly or treated as regular expression. Default is FALSE.
* ... Further arguments  to be passed to mcmc_pairs.

#### Details

For a detailed Description  see mcmc_pairs.

####  Examples
```{r}
## Not run:
fit <- brm(count ~ log_Age_c + log_Base4_c * Trt_c
+ (1|patient) + (1|visit),
data = epilepsy, family = "poisson")
pairs(fit, pars = parnames(fit)[1:3], exact_match = TRUE)
pairs(fit, pars = "^sd_")
## End(Not run)
```

