---
title: "``brms::posterior_interval.brmsfit``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(brms)
```

## ``posterior_interval.brmsfit``: Compute posterior uncertainty intervals

#### Description 
Compute posterior uncertainty intervals for brmsfit objects.

#### Usage
<pre><code>
## S3 method for class 'brmsfit'
posterior_interval(object, pars = NA, prob = 0.95,...)
</code></pre>

#### Arguments
* ``object`` An object of class brmsfit
* ``pars``: Names of parameters for which posterior samples should be returned, as given by a character vector or regular expressions. By default, all posterior samples of all parameters are extracted.
* ``prob``: A value between 0 and 1 indicating the desired probability to be covered by the uncertainty intervals. The default is 0.95.
* ``...``: More arguments passed to ``as.matrix.brmsfit``.
* ``Value``: A matrix with lower and upper interval bounds as columns and as many rows as selected parameters.

#### Examples
```{r}
## Not run:
fit <- brm(count ~ zAge + zBase * Trt,
data = epilepsy, family = negbinomial())
posterior_interval(fit)
## End(Not run)
```
