---
title: "``brms::predict.brmsfit``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(brms)
```



predict.brmsfit Model Predictions of brmsfit Objects

#### Description 

Predict responses based on the fitted model. Can be performed for the data used to fit the model
(posterior predictive checks) or for new data. By definition, these predictions have higher variance
than predictions of the fitted #### Values (i.e., the ’regression line’) performed by the fitted method.
This is because the measurement error is incorporated. The estimated means of both methods
should, however, be very similar.

#### Usage
<pre><code>
## S3 method for class 'brmsfit'
predict(object, newdata = NULL, re_formula = NULL,
transform = NULL, resp = NULL, negative_rt = FALSE,
nsamples = NULL, subset = NULL, sort = FALSE, ntrys = 5,
summary = TRUE, robust = FALSE, probs = c(0.025, 0.975), ...)
## S3 method for class 'brmsfit'
posterior_predict(object, newdata = NULL,
re_formula = NULL, re.form = NULL, transform = NULL, resp = NULL,
negative_rt = FALSE, nsamples = NULL, subset = NULL,
sort = FALSE, ntrys = 5, ...)
</code></pre>

#### Arguments

* object An object of class brmsfit.
* newdata An optional data.frame for which to evaluate predictions. If NULL (default), the
original data of the model is used.
* re_formula formula containing group-level effects to be considered in the prediction. If
NULL (default), include all group-level effects; if NA, include no group-level effects.
* transform A function or a character string naming a function to be applied on the predicted
responses before summary statistics are computed.
* `` resp``: Optional names of response variables. If specified, predictions are performed
only for the specified response variables.
* negative_rt Only relevant for Wiener diffusion models. A flag indicating whether response
times of responses on the lower boundary should be returned as negative #### Values.
This allows to distinguish responses on the upper and lower boundary. Defaults
to FALSE.
* nsamples Positive integer indicating how many posterior samples should be used. If NULL
(the default) all samples are used. Ignored if subset is not NULL.
subset A numeric vector specifying the posterior samples to be used. If NULL (the
default), all samples are used.
* sort Logical. Only relevant for time series models. Indicating whether to return
predicted values in the original order (FALSE; default) or in the order of the time
series (TRUE).
* ntrys Parameter used in rejection sampling for truncated discrete models only (defaults
to 5). See details for more information.
* summary Should summary statistics (i.e. means, sds, and 95% intervals) be returned instead
of the raw values? Default is TRUE.
* robust If FALSE (the default) the mean is used as the measure of central tendency and
the standard deviation as the measure of variability. If TRUE, the median and the
median absolute deviation (MAD) are applied instead. Only used if summary is
TRUE.

* probs The percentiles to be computed by the quantile function. Only used if summary is TRUE.
* `` ... ``: Further arguments passed to extract_draws that control several aspects of data
validation and prediction.
re.form Alias of re_formula.
#### Details
NA #### Values within factors in newdata, are interpreted as if all dummy variables of this factor are zero.
This allows, for instance, to make predictions of the grand mean when using sum coding.
Method posterior_predict.brmsfit is an alias of predict.brmsfit with summary = FALSE.
For truncated discrete models only: In the absence of any general algorithm to sample from truncated
discrete distributions, rejection sampling is applied in this special case. This means that #### Values
are sampled until a #### Value lies within the defined truncation boundaries. In practice, this procedure
may be rather slow (especially in R). Thus, we try to do approximate rejection sampling by sampling
each #### Value ntrys times and then select a valid #### Value. If all #### Values are invalid, the closest
boundary is used, instead. If there are more than a few of these pathological cases, a warning will
occur suggesting to increase argument ntrys.
#### Value
Predicted #### Values of the response variable. If summary = TRUE the output depends on the family:
For categorical and ordinal families, it is a N x C matrix, where N is the number of observations
and C is the number of categories. For all other families, it is a N x E matrix where E is equal
to length(probs) + 2. If summary = FALSE, the output is as a S x N matrix, where S is the
number of samples. In multivariate models, the output is an array of 3 dimensions, where the third
dimension indicates the response variables.

Examples
```{r}
## Not run:
## fit a model
fit <- brm(time | cens(censored) ~ age + sex + (1+age||patient),
data = kidney, family = "exponential", inits = "0")
## predicted responses
pp <- predict(fit)
head(pp)
```

```{r}
## predicted responses excluding the group-level effect of age
pp2 <- predict(fit, re_formula = ~ (1|patient))
head(pp2)
## predicted responses of patient 1 for new data
newdata <- data.frame(sex = factor(c("male", "female")),
age = c(20, 50),
patient = c(1, 1))
predict(fit, newdata = newdata)
## End(Not run)
```
