
## ``prior_samples.brmsfit`` 

Extract prior samples

#### Description 
Extract prior samples of specified parameters

#### Usage
<pre><code>
## S3 method for class 'brmsfit'
prior_samples(x, pars = NA, ...)
prior_samples(x, pars = NA, ...)
</code></pre>

#### Arguments

* ``x``: An R object typically of class ``brmsfit``
* ``pars``: Names of parameters for which prior samples should be returned, as given by a character vector or regular expressions. By default, all prior samples are extracted
* ``...``: Currently ignored


#### Examples
```{r}
fit <- brm(rating ~ treat + period + carry + (1|subject),
data = inhaler, family = "cumulative",
prior = set_prior("normal(0,2)", class = "b"),
sample_prior = TRUE)
# extract all prior samples
samples1 <- prior_samples(fit)
head(samples1)
```

```{r}
# extract prior samples for the population-level effects of 'treat'
samples2 <- prior_samples(fit, "b_treat")
head(samples2)
```

#### Details
To make use of this function, the model must contain samples of prior distributions. This can be ensured by setting ``sample_prior = TRUE`` in function ``brm()``. Currently there are methods for ``brmsfit`` objects.

#### Value
A data frame containing the prior samples.


#### Author(s)
Paul-Christian Buerkner <paul.buerkner@gmail.com>
