prior_samples.brmsfit 135
prior_samples.brmsfit Extract prior samples
#### Description 
Extract prior samples of specified parameters

#### Usage
<pre><code>
## S3 method for class 'brmsfit'
prior_samples(x, pars = NA, ...)
prior_samples(x, pars = NA, ...)
</code></pre>

#### Arguments

* x An R object typically of class brmsfit
* pars Names of parameters for which prior samples should be returned, as given by
* a character vector or regular expressions. By default, all prior samples are extracted
* ... Currently ignored

#### Details
To make use of this function, the model must contain samples of prior distributions. This can be
ensured by setting sample_prior = TRUE in function brm. Currently there are methods for brmsfit
objects.
#### Value
A data frame containing the prior samples.

#### Examples
```{r}
## Not run:
fit <- brm(rating ~ treat + period + carry + (1|subject),
data = inhaler, family = "cumulative",
prior = set_prior("normal(0,2)", class = "b"),
sample_prior = TRUE)
# extract all prior samples
samples1 <- prior_samples(fit)
head(samples1)
```

```{r}
# extract prior samples for the population-level effects of 'treat'
samples2 <- prior_samples(fit, "b_treat")
head(samples2)
## End(Not run)
```


Author(s)
Paul-Christian Buerkner <paul.buerkner@gmail.com>
