
pp_mixture.brmsfit Posterior Probabilities of Mixture Component Memberships
#### Description 
Compute the posterior probabilities of mixture component memberships for each observation including
uncertainty estimates.


#### Usage
<pre><code>
## S3 method for class 'brmsfit'
pp_mixture(x, newdata = NULL, re_formula = NULL,
resp = NULL, nsamples = NULL, subset = NULL, log = FALSE,
summary = TRUE, robust = FALSE, probs = c(0.025, 0.975), ...)
pp_mixture(x, ...)
</code></pre>

#### Arguments
* x An R object usually of class brmsfit.
* newdata An optional data.frame for which to evaluate predictions. If NULL (default), the
original data of the model is used.
* re_formula formula containing group-level effects to be considered in the prediction. If
NULL (default), include all group-level effects; if NA, include no group-level effects.
* `` resp``: Optional names of response variables. If specified, predictions are performed
only for the specified response variables.
* nsamples Positive integer indicating how many posterior samples should be used. If NULL
(the default) all samples are used. Ignored if subset is not NULL.
* subset A numeric vector specifying the posterior samples to be used. If NULL (the
default), all samples are used.
* log Logical; Indicates whether to return probabilities on the log-scale.
* summary Should summary statistics (i.e. means, sds, and 95% intervals) be returned instead
of the raw #### Values? Default is TRUE.
* robust If FALSE (the default) the mean is used as the measure of central tendency and the standard deviation as the measure of variability. If TRUE, the median and the
median absolute deviation (MAD) are applied instead. Only used if summary is TRUE.
* probs The percentiles to be computed by the quantile function. Only used if summary is TRUE.
* `` ... ``: Further arguments passed to extract_draws that control several aspects of data
validation and prediction.

#### Details
The returned probabilities can be written as P(Kn = kjY n), that is the posterior probability that
observation n originates from component k. They are computed using Bayes’ Theorem
P(Kn = kjY n) = P(Y njKn = k)P(Kn = k)=P(Y n);
where P(Y njKn = k) is the (posterior) likelihood of observation n for component k, P(Kn = k)
is the (posterior) mixing probability of component k (i.e. parameter theta<k>), and
P(Y n) =
X
(k = 1; :::;K)P(Y njKn = k)P(Kn = k)
is a normalizing constant.

#### Value
If summary = TRUE, an N x E x K array, where N is the number of observations, K is the number
of mixture components, and E is equal to length(probs) + 2. If summary = FALSE, an S x N x
K array, where S is the number of posterior samples.

#### Examples

```{r}
## Not run:
## simulate some data
set.seed(1234)
dat <- data.frame(
y = c(rnorm(100), rnorm(50, 2)),
x = rnorm(150)
)
```

```{r}
## fit a simple normal mixture model
mix <- mixture(gaussian, nmix = 2)
prior <- c(
prior(normal(0, 5), Intercept, nlpar = mu1),
prior(normal(0, 5), Intercept, nlpar = mu2),
prior(dirichlet(2, 2), theta)
)
fit1 <- brm(bf(y ~ x), dat, family = mix,
prior = prior, chains = 2, inits = 0)
summary(fit1)
## compute the membership probabilities
ppm <- pp_mixture(fit1)
str(ppm)
## extract point estimates for each observation
head(ppm[, 1, ])
## classify every observation according to
## the most likely component
apply(ppm[, 1, ], 1, which.max)
## End(Not run)
```

