---
title: "``brms::cor_arr``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(brms)
```



cor_arr ARR(r) correlation structure

#### Description 

This function is a constructor for the cor_arma class allowing for autoregressive effects of the
response only.

#### Usage

<pre><code>
cor_arr(formula = ~1, r = 1)
</code></pre>

#### Arguments
* formula A one sided formula of the form ~ t, or ~ t | g, specifying a time covariate t and, optionally, a grouping factor g. A covariate for this correlation structure
must be integer valued. When a grouping factor is present in formula, the correlation structure is assumed to apply only to observations within the same
grouping level; observations with different grouping levels are assumed to be uncorrelated. Defaults to ~ 1, which corresponds to using the order of the
observations in the data as a covariate, and no groups.
* r A non-negative integer specifying the autoregressive response (ARR) order of the ARMA structure. Default is 1.

#### Examples

```{r}
cor_arr(~visit|patient, r = 2)
```

#### Details
AR refers to autoregressive effects of residuals, which is what is typically understood as autoregressive
effects. However, one may also model autoregressive effects of the response variable, which is
called ARR in brms.

#### Value
An object of class cor_arma containing solely autoregressive response terms.

