---
title: "``brms::epilepsy``"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(brms)
library(janitor)
library(magrittr)
library(dplyr)
```

Epileptic seizure counts

#### Description 
Breslow and Clayton (1993) analyze data initially provided by Thall and Vail (1990) concerning seizure counts in a randomized trial of anti-convulsant therapy in epilepsy. Covariates are treatment,
8-week baseline seizure counts, and age of the patients in years.

```{r}
head(epilepsy)

```

```{r}
epilepsy %>% tabyl(Age,Trt)
```

#### Format

A dataframe of 236 observations containing information on the following 9 variables.

* ``Age``: The age of the patients in years
* ``Base``: The seizure count at 8-weeks baseline
* ``Trt``: Either 0 or 1 indicating if the patient received anti-convulsant therapy
* ``zAge``: The logarithm of Age centered around its mean
* ``zBase``: The logarithm of Base divided by 4 (i.e. log(Base/4)) centered around its mean
* ``Trt``: Trt centered around its mean
* ``visit``: The session number from 1 (first visit) to 4 (last visit)
* ``count``: The seizure count between two visits
* ``patient``: The patient number
* ``obs``: The observation number, i.e. a unique identifier for each observation


#### Examples
```{r}

## poisson regression without random effects.
fit1 <- brm(count ~ zAge + zBase * Trt,
  data = epilepsy, family = poisson())
summary(fit1)
```
```{r}
plot(fit1)
```

```{r}
## poisson regression with random intercepts of patients and visits
## as well as normal priors for fixed effects parameters.
fit2 <- brm(count ~ zAge + zBase * Trt
+ (1|patient) + (1|visit),
data = epilepsy, family = poisson(),
prior = set_prior("normal(0,5)"))
```

```{r}
summary(fit2)
plot(fit2)

```
