---
title: "summary_inhaler"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(brms)
library(janitor)
library(magrittr)
library(dplyr)
```

## ``inhaler ``

Clarity of inhaler instructions

#### Description 
Ezzet and Whitehead (1991) analyze data from a two-treatment, two-period crossover trial to compare 2 inhalation devices for delivering the drug salbutamol in 286 asthma patients. Patients were asked to rate the clarity of leaflet instructions accompanying each device, using a 4-point ordinal scale.

```{r}
head(inhaler)
```

#### Format
A dataframe of 572 observations containing information on the following 5 variables.
* ``subject``: The subject number
* ``rating``: The rating of the inhaler instructions on a scale ranging from 1 to 4 
* ``treat``: A contrast to indicate which of the two inhaler devices was used
* ``period``: A contrast to indicate the time of administration 
* ``carry``: A contrast to indicate possible carry over effects


### Examples
```{r}
## ordinal regression with family "sratio"
fit1 <- brm(rating ~ treat + period + carry,
            data = inhaler, family = sratio(),
            prior = set_prior("normal(0,5)"))
summary(fit1)
plot(fit1)
```

```{r}
## ordinal regression with family "cumulative"
## and random intercept over subjects
fit2 <- brm(rating ~ treat + period + carry + (1|subject),
            data = inhaler, family = cumulative(),
            prior = set_prior("normal(0,5)"))
summary(fit2)
plot(fit2)
```
